An upper bound to gas delivery via pressure-swing adsorption in nanoporous materials

### 2020-05-11 gas-adsorption/gas-ads-body.tex
checkout all of the calculations and removed comments that were answered.

Figure~\ref{fig:methane-298-D} shows the upper bound for methane storage at room temperature~(374~cm$^3$~STP/cm$^3$). In addition to the predicted maximum deliverable capacity as a function of \gst,
\corysays{subtlety here: isnt ur proof restricted to saying $\V_{opt}$ provides the upper bound? does it really prove that, for fixed and nonoptimal $\gst$, a spatially uniform potential is optimal over a non-spatially uniform one? I don't think it does...}
the ARPA-E target of 315~cm$^3$~STP/cm$^3$~\cite{arpaemove} is shown for context. For an adsorbent with at least 84\% void fraction, the ARPA-E target is theoretically possible. The experimental deliverable capacities of several adsorbents~\cite{mason2014evaluating} are also shown over a range of $\gst$ (converted from the measured adsorption isotherm as explained in \davidsays{confirm this} Sec.~\ref{sec:phi-is-delta-g}). These can be compared with the highest observed deliverable capacities for methane at room temperature in rigid materials, up to 208~cm$^3$~STP/cm$^3$~\cite{simon2015materials}. 
% don't think the below is helpful or correct: Gst opt is reached by some... there are void fraction constraints too.
% To reach the ARPA-E target, an adsorbent material with a higher $|\gst|$ would need to be found.

@@

\jpsays{I edited everything below this comment. The original is commented out}

Storage of hydrogen is considerably more challenging owing to its relatively weak interaction with adsorbents. The DOE ULTIMATE deliverable capacity target~\cite{DOE} is within 6\% of the upper bound at 25$^\circ$C \red{check}. Figure~\ref{fig:hydrogen-298-D} shows the theoretical upper bound curve for hydrogen storage along with a range of experimental measurements for known MOFs.  The DOE ULTIMATE deliverable capacity target is theoretically possible, however by such a small margin that we can safely rule out the possibility of reaching this target through storage and delivery of hydrogen in \emph{any} rigid substrate at room temperature. Such a material would require a void fraction of at least 94\% \red{check}. On top of this, the DOE ULTIMATE target requires an optimal $|\gst|$ of 10~kJ/mol which is far greater than what is found in observed porous materials. This reflects the known fact that hydrogen interacts with substrates far more weakly than methane does. One possibility that has been pursued is storage at cryogenic temperatures. See Section~\ref{sec:cryo-hydrogen} in the Supplementary Information for the upper bound for storage of hydrogen at 77 K.

@@

\section{Conclusion}
We have established an upper bound on the deliverable capacity via pressure-swing adsorption in rigid porous solids based on experimentally measured properties of pure gases. While these upper bounds do not rule out the discovery of materials that reach current DOE targets, they cast strong doubt on the possibility of achieving these goals when we consider the additional constraints imposed due to steric hindrance between substrate atoms and the adsorbate. Our upper bound does indicate that those goals cannot be exceeded by more than 19\% for methane and 6\% for hydrogen \red{check}. Fortunately, there are some limitations to these upper bounds which suggest avenues for future developments which could allow the targets to be met.

>>>>

Figure~\ref{fig:methane-298-D} shows the upper bound for methane storage at room temperature~(374~cm$^3$~STP/cm$^3$). In addition to the predicted maximum deliverable capacity as a function of \gst,
\corysays{subtlety here: isnt ur proof restricted to saying $\V_{opt}$ provides the upper bound? does it really prove that, for fixed and nonoptimal $\gst$, a spatially uniform potential is optimal over a non-spatially uniform one? I don't think it does...}
the ARPA-E target of 315~cm$^3$~STP/cm$^3$~\cite{arpaemove} is shown for context. For an adsorbent with at least 84\% void fraction, the ARPA-E target is theoretically possible. The experimental deliverable capacities of several adsorbents~\cite{mason2014evaluating} are also shown over a range of $\gst$ (converted from the measured adsorption isotherm as explained in Sec.~\ref{sec:phi-is-delta-g}). These can be compared with the highest observed deliverable capacities for methane at room temperature in rigid materials, up to 208~cm$^3$~STP/cm$^3$~\cite{simon2015materials}. 
% don't think the below is helpful or correct: Gst opt is reached by some... there are void fraction constraints too.
% To reach the ARPA-E target, an adsorbent material with a higher $|\gst|$ would need to be found.

@@

Storage of hydrogen is considerably more challenging owing to its relatively weak interaction with adsorbents. The DOE ULTIMATE deliverable capacity target~\cite{DOE} is within 6\% of the upper bound at 25$^\circ$C. Figure~\ref{fig:hydrogen-298-D} shows the theoretical upper bound curve for hydrogen storage along with a range of experimental measurements for known MOFs.  The DOE ULTIMATE deliverable capacity target is theoretically possible, however by such a small margin that we can safely rule out the possibility of reaching this target through storage and delivery of hydrogen in \emph{any} rigid substrate at room temperature. Such a material would require a void fraction of at least 94\%. On top of this, the DOE ULTIMATE target requires an optimal $|\gst|$ of 10~kJ/mol which is far greater than what is found in observed porous materials. This reflects the known fact that hydrogen interacts with substrates far more weakly than methane does. One possibility that has been pursued is storage at cryogenic temperatures. See Section~\ref{sec:cryo-hydrogen} in the Supplementary Information for the upper bound for storage of hydrogen at 77 K.

@@

\section{Conclusion}
We have established an upper bound on the deliverable capacity via pressure-swing adsorption in rigid porous solids based on experimentally measured properties of pure gases. While these upper bounds do not rule out the discovery of materials that reach current DOE targets, they cast strong doubt on the possibility of achieving these goals when we consider the additional constraints imposed due to steric hindrance between substrate atoms and the adsorbate. Our upper bound does indicate that those goals cannot be exceeded by more than 16\% for methane and 6\% for hydrogen. Fortunately, there are some limitations to these upper bounds which suggest avenues for future developments which could allow the targets to be met.
